
---
title: "bellabeat_project"
author: "Priyanka Dwivedi"
date:   "07/02/22"
output: html_document
---

## Introduction
explores smart device user's daily habits by using **public data-
FitBit Fitness Tracker Data**. This Kaggle data set contains personal fitness tracker from thirty fitbit users. It includes information about daily activity, steps, and weight information that can be used to explore user's habits.

### Objective
* Analyze smart device usage data in order to gain insight.
* Identify some trends in smart device usage.
* How could these trends apply to Bellabeat customers?

### Prepare Data

```{r}
install.packages("tidyverse")
library(tidyverse)
library(ggplot2)
library(dplyr)
library(readr)
```
```{r warning=FALSE, echo=FALSE,results='hide'}
read.csv("dailyActivity_merged.csv")
read.csv("sleepDay_merged.csv")
read.csv("weightLogInfo_merged.csv")

```
### Processing of data
```{r warning=FALSE}
daily_activity<- read.csv("dailyActivity_merged.csv")
```
```{r warning=FALSE}
sleep_day<- read.csv("sleepDay_merged.csv")
```
```{r warning=FALSE}
weight_loginfo<- read.csv("weightLogInfo_merged.csv")
```
### analysis of data
```{r}
Daily_Activity<- select(daily_activity, Id, TotalDistance, SedentaryMinutes)
```
```{r}
Weight<- distinct(weight_loginfo, Id, WeightKg)
```
```{r}
Sleep<- select(sleep_day,Id, TotalSleepRecords, TotalMinutesAsleep, TotalTimeInBed)
```
```{r}
combined<- merge(Daily_Activity, Weight)
combined_full_data<- merge(combined, Sleep)
```
### Realtion between distance covered by person and sleep

```{r}
ggplot(data=combined_full_data)+
  geom_point(mapping=aes(x=TotalDistance, y=TotalMinutesAsleep,color=TotalMinutesAsleep))+
  geom_smooth(mapping=aes(x=TotalDistance, y=TotalMinutesAsleep),color="purple")+
  labs(title="Relation between Distance covered and Sleep")
```


If some distance cover daily  by person then their sleep is also balanced.
___________________________________________________________________________________

### Relation between sedentary time and weight
```{r}
ggplot(data=combined_full_data)+
  geom_smooth(mapping=aes(x=SedentaryMinutes, y=WeightKg),color="black")+
  labs(title="Relation between sedentary time and weight of person")+
  geom_point(mapping=aes(x=SedentaryMinutes, y=WeightKg, color=WeightKg))

```


if *Sedentary time of person is less then their weight is balanced.*
___________________________________________________________________________________

### Relation between distance covered and weight

```{r}
ggplot(data=combined_full_data)+
  geom_smooth(mapping=aes(x=TotalDistance, y=WeightKg),color="black")+
  labs(title="Relation between weight and distance covered daily")
  
```



if distance is covered daily then *person is active then weight is also balanced*.
___________________________________________________________________________________

### Conclusion 
If person is active and cover some distance daily and  their sedentary time is less hen their sleep and weight both are balanced and person is healthy.



